Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-03-14 paperDistance/paper.tex
assumptions draft:

We make the following assumptions. The method we present is correct and justifiable under these assumptions, each of which is questionable in its own right. We return to criticize these assumptions---and the method that flows from them---in the Discussion below.
\begin{itemize}
\item Some kind of stationarity assumption.
\item Our empirical bayes approach is ok---that is, our numbers are large enough.
\item The photometric uncertainties in the J band are small compared with the uncertainties in the parallax; the uncertainties are gaussian
\item Mixture-of-gaussian model with fixed number of gaussians
\item no use of physical models, baby!
\end{itemize}

>>>>

We make the following assumptions. The method we present is correct
and justifiable under these assumptions, each of which is questionable
in its own right. We return to criticize these assumptions---and the
method that flows from them---in the Discussion below.
\begin{itemize}
\item We make an assumption of \emph{stationarity}; that is, that the
  stars measured at lower signal-to-noise have analogs measured at
  higher signal-to-noise.  In detail, this assumption is wrong, of
  course (for example, distant halo stars are different than local
  disk stars), but the stationarity assumption is fairly weak; as long
  as there is support in the high signal-to-noise stars for the types
  of stars seen at low signal-to-noise, the results will not be
  strongly biased, but this assumption is deep and fundamental to this
  work.
\item We assume that we have large numbers of stars, large enough that
  an empirical-Bayes or maximum-marginalized likelihood is a safe
  approximation to full Bayesian inference. This assumption will be
  least true in the least-populated parts of the \cmd. In the extreme
  case of a stellar type with only one (statistically distinct)
  exemplar in the data set, this assumption will be maximally wrong.
\item We assume that the \tgas\ parallax uncertainties dominate the
  noise in any estimates of absolute magnitude. We further assume that
  the parallax and color uncertainties are Gaussian in form with
  correctly known variances. In detail, we assume that the [INSERT
    CORRECT TERMINOLOGY FROM GAIA HERE] parallax uncertainty estimates
  are correct. Here we are making use of the fact that, for
  de-noising, under-estimation of measurement noise is conservative
  (it leads to under-deconvolution).
\item We assume that the \cmd\ can be represented with a mixture of
  Gaussians in a particular transformed space. This mixture we fix
  (with only heuristic analysis) at 128, 512, and 2048 Gaussians in
  different experiments.
\item We make no use of stellar models; our only assumptions about
  stellar physics are generic and implicit (for example, that the
  \cmd\ is somehow smooth and compact).
\end{itemize}
